\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}

\name{Jeffrey Sardella}
\address{Rocklin, CA \\ (916) 295-3636}
\address{sardellajeffrey123@gmail.com \\ github.com/JeffreySardella \\ sardella.dev}

\begin{document}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{SUMMARY}
Computer Science professional with over 6 years of technical experience in object-oriented programming (C\#) and 4 years of data-driven development (Python, SQL). Proven track record building multi-tier applications, REST APIs, and automation tools across web, mobile, and Discord platforms. Seeking full-stack or backend roles in .NET and React stacks.
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}
\textbf{Languages:} C\# (6 yrs), Python (4 yrs), SQL (3+ yrs), JavaScript (2+ yrs), Java, PHP, R, HTML/CSS \\
\textbf{Frameworks:} ASP.NET \& .NET Core, React, Vue.js, Flutter, Tailwind CSS, Bootstrap, pandas, NumPy \\
\textbf{Databases \& APIs:} SQL Server (Relational modeling, Stored Procedures), SQLite, RESTful APIs, Auth/RBAC \\
\textbf{Tools \& Cloud:} Git, GitHub, Visual Studio, VS Code, Postman, Agile/Scrum, Azure Fundamentals, Claude Code
\end{rSection}

%----------------------------------------------------------------------------------------
% SOFTWARE ENGINEERING EXPERIENCE (PROJECT-BASED)
%----------------------------------------------------------------------------------------

\begin{rSection}{SOFTWARE ENGINEERING EXPERIENCE (PROJECT-BASED)}

\textbf{Full-Stack Developer | Medical Web Application} \hfill Jan 2024 -- May 2024
\begin{itemize}
    \item Led backend development on a 6-person team; drove the majority of commits across patient management, appointments, prescriptions, medical records, and secure in-app messaging.
    \item Engineered a multi-tier \textbf{ASP.NET MVC} / \textbf{C\#} application with a DAL pattern; designed and normalized a \textbf{SQL Server} schema using stored procedures for performance and security.
    \item Implemented role-based auth (doctor, worker, patient) with OTP email confirmation and built \textbf{Bootstrap}/Razor Pages frontend views.
\end{itemize}

\textbf{Backend Developer | OWP Forum Web Application} \hfill Jan 2025 -- Present
\begin{itemize}
    \item Building a \textbf{RESTful API} with \textbf{PHP Slim} for a real-world client (Sacramento State OWP), supporting CRUD operations across a four-tier role system (Admin, Moderator, User, Guest).
    \item Architecting a \textbf{T-SQL} relational database with OTP email auth and custom middleware for permission-based route protection.
    \item Collaborating in an 8-person \textbf{Agile/Scrum} team with bi-weekly client meetings; integrating \textbf{Vue.js} frontend with WCAG-compliant responsive design.
\end{itemize}

\textbf{Developer | Discord Voice Word Tracker} \hfill 2025
\begin{itemize}
    \item Built a Discord bot in \textbf{Python} using \textbf{Pycord} that captures per-user audio streams and transcribes speech entirely on-device via \textbf{Faster-Whisper} — no external APIs.
    \item Posts per-user word counts and top 10 most-used words to a text channel at session end.
\end{itemize}

\textbf{Developer | PogoFest Ticket Alerts Discord Bot} \hfill 2025 -- Present
\begin{itemize}
    \item Built a Discord bot that scrapes the Pok\'{e}mon GO site every 3 minutes with \textbf{aiohttp} and \textbf{BeautifulSoup4}, instantly alerting servers when GO Fest tickets go on sale.
    \item Designed a \textbf{SQLite}-backed per-server config system with custom alert channels and role pings via slash commands.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFESSIONAL EXPERIENCE}

\textbf{IT Assistant \& Operations Support} \hfill Jan 2021 -- Jun 2021 \\
Pool Time Pool and Spa -- Rancho Cordova, CA
\begin{itemize}
    \item Configured software to streamline job estimates and transitioned paper records to searchable digital formats.
    \item Provided technical support for Windows systems to maintain department productivity.
\end{itemize}

\textbf{Shift Manager} \hfill Nov 2016 -- Dec 2020 \\
Burger and Cream -- Auburn, CA
\begin{itemize}
    \item Supervised diverse teams and managed daily operations in a high-volume environment.
    \item Troubleshot POS systems and technical equipment to minimize service disruptions.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}
\textbf{Bachelor of Science, Computer Science} \hfill Expected Spring 2026 \\
California State University, Sacramento \\

\textbf{Associate of Science, Computer Science} \hfill 2023 \\
Sierra College
\end{rSection}

\end{document}
